Technical Report

### 2018-01-19 fully-abstract-comp/technical-report.tex
Replied to Dominiques comments (and made a few corrections based on them).

\subsection{Future world}

For both $\privft$ and $\pubft$ we have
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
            { W' \future W }
\end{mathpar}
%
The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$:
\begin{mathpar}
  \inferrule{ }
  { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi_\pub,\phi,H) \privft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
%
Public future regions are allowed to transition according to the public part of their transition system.
\begin{mathpar}
    \inferrule{ }
            { \revoked \pubft \revoked }
\and
  \inferrule{ (s,s') \in \phi_\pub }
            { (v,s',\phi_\pub,\phi,H) \pubft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}

@@

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\})(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\oplus W_\lrk \oplus W_\lrr \oplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfaction does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}
\dominique{18-1-2018: Lau, I suppose the above has been answered verbally already during one of the previous skype calls, but for reference, this is what the spatial vs spatial_owned distinction is intended to solve: the world will contain spatial regions for such memory segments, but not spatial_owned ones, so the memory satisfaction will require the memory to be present but not allow it to be addressed.}
\dominique{18-1-2018: $W_\lrk$, $k_{d,*}$, $k_{c,*}$ can all be removed from the above definition now, right?}

\[
  \lro(W) = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n, \src{\ms_{f,S}}, \ms_{f,T} \ldotp \\
      \quad \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\ms_T \uplus \ms_{f,T},\reg_T) \term\\
      \quad \tand\\
      \quad (\ms_T \uplus \ms_{f,T},\reg_T) \term[i] \Rightarrow \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

@@

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : (\RegName \setminus (\{\pcreg \} \cup R))\fun \World \ldotp \\
      \quad W = \bigoplus_{r \in (\RegName\setminus (\{\pcreg \} \cup R))} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
% DOMI 18-1-2018: the below remark is obsolete, so I commented it out.
% Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
\dominique{18-1-2018: it might be convenient to exclude $\rdata$ from the $\lrr$ relation by default too. Check if we ever use it with other instantiations of R.}

@@

      \npair{(\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr),\sealed{\sigma,\vsc_C})} \in \lrp(W)

@@

      \quad \npair{\left[\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,((\rw,\linear),\baddr,\eaddr,\baddr)}\endarray\right)\right]} \in \lrp(W') \wedge \\

@@

      \quad \memSat[n']{\stpair[.]{\ms_S,(\ms_f,\opc)::\stk,\ms_\stk}{\ms_T}}{W_\lrm}} \wedge \\
      \quad \npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata,\rstk,\rtmp{1},\rtmp{2}\})(W_\lrr) \wedge \\

@@

      \qquad \quad \npair[n']{\left(\array{l}(\ms_S,\reg_S\updReg{\rstk,\pcreg,\rdata,\rtmp{1},\rtmp{2}}{\stkptr{\rw,\stkb,\eaddr,\baddr},((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),0,0,0},\stk,\ms_\stk \uplus \ms_f),\\
                                             (\ms_T,\reg_S\updReg{\rstk,\pcreg,\rdata,\rtmp{1},\rtmp{2}}{((\rw,\linear),\stkb,\eaddr,\baddr),((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C+?)})

>>>>

\subsection{Future world}
For both $\privft$ and $\pubft$ we have
\begin{mathpar}
  \inferrule{ \exists m : \RegionName \fun \RegionName, \text{ injective}\ldotp \dom(W') \supseteq \dom(m(W)) \wedge \forall r \in \dom(W)\ldotp W'(m(r)) \future W(r) }
            { W' \future W }
\end{mathpar}
%
The private future regions allow transitions in the private part of the transition system. They also allow $\spatial$ regions to become $\revoked$:
\begin{mathpar}
  \inferrule{ }
  { \revoked \privft (\spatial,\_,\_,\_,\_)}
\and
  \inferrule{ }
            { \revoked \privft \revoked }
\and
  \inferrule{ (s,s') \in \phi }
            { (v,s',\phi_\pub,\phi,H) \privft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}
%
Public future regions are allowed to transition according to the public part of their transition system.
\begin{mathpar}
    \inferrule{ }
            { \revoked \pubft \revoked }
\and
  \inferrule{ (s,s') \in \phi_\pub }
            { (v,s',\phi_\pub,\phi,H) \pubft (v,s,\phi_\pub,\phi,H)  }
\end{mathpar}

@@

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{[\stpair[.]{v_{c,S}}{v_{c,T}},\stpair[.]{v_{d,T}}{v_{d,S}}]} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata}{v_{c,S},v_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata}{v_{c,T},v_{d,T}})
                       \endarray\right)}
      \in \lro(W \oplus W_\lrr \oplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but if you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfaction does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}
\dominique{18-1-2018: Lau, I suppose the above has been answered verbally already during one of the previous skype calls, but for reference, this is what the spatial vs spatial\_owned distinction is intended to solve: the world will contain spatial regions for such memory segments, but not spatial\_owned ones, so the memory satisfaction will require the memory to be present but not allow it to be addressed.}
\dominique{18-1-2018: $W_\lrk$, $k_{d,*}$, $k_{c,*}$ can all be removed from the above definition now, right?}
\lau{19-01-2018: Yes. And I have removed them}
\[
  \lro(W) = \left\{ \npair{\left(\array{l}\src{(\ms_S,\reg_S,\stk_S,\ms_{\stk,S})},\\(\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \forall i \leq n, \src{\ms_{f,S}}, \ms_{f,T} \ldotp \\
      \quad \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term[i] \Rightarrow (\ms_T \uplus \ms_{f,T},\reg_T) \term\\
      \quad \tand\\
      \quad (\ms_T \uplus \ms_{f,T},\reg_T) \term[i] \Rightarrow \src{(\ms_S \uplus \ms_{f,S},\reg_S,\stk_S,\ms_{\stk,S})} \term
    \end{array}
\right\}
\]

@@

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : (\RegName \setminus (\{\pcreg \} \cup R))\fun \World \ldotp \\
      \quad W = \bigoplus_{r \in (\RegName\setminus (\{\pcreg,\rdata \} \cup R))} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
We write $\lrr(W)$ to mean $\lrr(\emptyset)(W)$. That is, if we do not need to exclude extra registers, then we simlpy omit that argument.
% DOMI 18-1-2018: the below remark is obsolete, so I commented it out.
% Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
%\dominique{18-1-2018: it might be convenient to exclude $\rdata$ from the $\lrr$ relation by default too. Check if we ever use it with other instantiations of R.}
% Lau 19-01-2018: Added rdata as default.

@@

      \npair{([\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr),\sealed{\sigma,\vsc_C})]} \in \lrp(W)

@@

      \quad \npair[n']{\left[\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,((\rw,\linear),\baddr,\eaddr,\baddr)}\endarray\right)\right]} \in \lrp(W') \wedge \\

@@

      \quad \memSat[n']{\stpair[.]{\ms_S,(\ms_f,\opc)::\stk,\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \quad \npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rtmp{1},\rtmp{2}\})(W_\lrr) \wedge \\

@@

      \qquad \quad \npair[n']{\left(\arraycolsep=0pt\array{l}
                                     \left(\arraycolsep=0pt\array{l}\ms_S,\reg_S \left[
                                       \array{l}\reg.\rstk,\pcreg,\rdata,\rtmp{1},\rtmp{2}\mapsto\\\stkptr{\rw,\stkb,\eaddr,\baddr},((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C),0,0,0\endarray \right]\\
                                     ,\stk,\ms_\stk \uplus \ms_f
                                     \endarray \right),\\
                                             \left(\ms_T,\reg_S\left[\array{l}\reg.\rstk,\pcreg,\rdata,\rtmp{1},\rtmp{2}\mapsto\\((\rw,\linear),\stkb,\eaddr,\baddr),((\perm_C,\lin_C),\baddr_C,\eaddr_C,\aaddr_C+?),0,0,0\endarray\right]\right)
